---
title: "Internet Redlining"
author: "Neha, Aidan, and David"
date: "11/13/2022"
output: html_document
---


library(knitr)
```{r, message = FALSE, echo = FALSE, warning = FALSE}
library("tidyverse")
library("plotly")
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
This is a brief report regarding internet redlining for interent services provided by AT&T specifically based on data from a study conducted by _The MarkUp_. This report explores relationships between different socio-economic disparities such as race and household income with speed and price of internet services. ([source](https://github.com/the-markup/investigation-isp)).
The data reveals that the maximum download speed provided by AT&T was 'r max_download_speed_ATT' , while the maximum upload speed provided by AT&T was 
'r max_upload_speed_ATT'. The lowest speed of internet service provided in non-white areas by AT&T was 'r lowest_speed_in_non_white_location_ATT'. 

Here are the locations which experienced the lowest internet redlining by AT&T 'r locations_with_lowest_Redlining_Grade_ATT'. 



* Please see Canvas for more details.

## Data_summary_in_nation
Here is the mean data of AT&T group by state.

```{r, message = FALSE, echo = FALSE, warning = FALSE}
source("../source/B3.R")
data_in_nation
```

The data of mean Internet record on national level. The data is categorize by state.It includes the race percentage and redlining grade in contrast to Internet speed which present the economic imbalance in different regions. This chart implies the inequality treatment and economic gap in different regions.

## Type of internet most often used

This pie chart shows the distributions of the different kinds of internet most used: Copper, Fiber, Fiber Based, Not Fiber. 


```{r, message = FALSE, echo = FALSE, warning = FALSE}
source("../source/B6.R")
pie_total
```

This chart shows the distribution of the types of internet used across America. In the future, we will have this data be able to be segmented by state, so users can choose a state that they want to inspect. 

(The graph will not show up since our CSV data cannot be read. We will ask about that issue in section)


## Internet speed for each provider
Here's a barchart showing the up and download speed:
```{r, message = FALSE, echo = FALSE, warning = FALSE}
source("../source/B5.R")
ISP_Speeds_plot
```
This chart is a bar chart that, based on who the provider is, shows the average upload and download speed across all the data we have. This chart is also interactive, when you hover over each column, you can see the exact upload and download speed. This chart allows users to see which Internet Service Providers (ISPs) have the fastest average internet.


## Internet speed distributions based on redlining
To visually identify disparities in internet speeds by redlining level, here is a choropleth math that visualizes the percentage point difference of lower income areas with slower internet speeds:

```{r, message = FALSE, echo = FALSE, warning = FALSE}
source("../source/B4.R")
plot_choropleth
```
This data visualization includes a choropleth map that displays the percentage point difference of lower income areas across the country with slower internet speeds. This chart allows users to visualize the overall impacts of internet redlining across the country through a scale of redlining grades represented by varying shades of blue. A lighter shade of blue represents less internet redlining, whereas a darker shade represents a higher level of internet redlining and grey represents areas where the data was "NA". 
